JavaScript as an Embedded DSL

### 2012-03-26 papers/ecoop2012/article.tex
grammar

>>>>

Our implementation of continuations is an example of an interesting technique of applying selective cps
transformation to embedded DSLs by means of a deep linguistic reuse, exploiting a host language feature to
implement the corresponding DSL feature without (much) additional work. An interesting insight is that CPS
transforming a program generator allows it to generate code that is in CPS.
